¿Qué pueden hacer las escuelas para disminuir la desigualdad en el conocimiento cívico?

### 2020-08-22 docs/paper.Rmd
Ediciones

---
title: "¿Qué pueden hacer las escuelas para disminuir la desigualdad en el conocimiento cívico?"
author: "Yanara Jerez, Adonai Arancibia, Anais Herrera, Francisco Meneses y Victor Jimenez"
date: "31 de julio de 2020"
output:
  html_document:
     theme: united
     highlight: tango
     toc: true
     toc_float: true
     toc_depth: 2
     number_sections: false
     code_folding: show
bibliography: 
  - "../input/bib/Mi_biblioteca.bib"
cls: "../input/bib/apa6.cls"
linkcolor: blue
link-citations: yes
---

@@

## _Nivel 2: Variables independientes_

  a. __S_VALPARTS: Cultura participativa de los estudiantes [AGREGADA]: How much do you agree or disagree with the following statements about student participation at school?__ (1 = Strongly agree, 2 = Agree, 3 = Disagree, 4 = Strongly disagree, 7 = Invalid, 8 = Not administered, 9 = Omitted)

      * IS3G21A: Student participation in how schools are run can make schools better.

      * IS3G21B: Lots of positive changes can happen in schools when students work together.

      * IS3G21C: Organizing groups of students to express their opinions could help solve problems in schools.

      * IS3G21D: Students can have more influence on what happens in schools if they act together rather than alone.

      * IS3G21E: Voting in student elections can make a difference to what happens at schools.

@@

![Distribución del conocimiento cívico](../output/graphs/histograma.png)

@@

![Relación entre las variables](../output/graphs/corrplot.png)

@@

```{r results='asis'}
library(texreg)
load(file = "../output/graphs/model_nulo.Rdata")
htmlreg(results_0)

@@

![Influencia de la socialización de la familia y la escuela](../output/graphs/reg1.png)

@@

```{r results='asis'}
library(texreg)

@@

![Interacción entre conocimiento cívico y nivel socioeconómico del estudiante y colegio](../output/graphs/interaccion.png)

>>>>

---
title: "¿Qué pueden hacer las escuelas para disminuir la desigualdad en el conocimiento cívico?"
author: "Autores: Anais Herrera, Francisco Meneses, Victor Jimenez, Alejandra Delaveau y Catalina Flores Editores: Yanara Jerez, Adonai Arancibia, Anais Herrera, Francisco Meneses y Victor Jimenez"
date: "21 de agosto de 2020"
output:
  html_document:
     theme: united
     highlight: tango
     toc: true
     toc_float: true
     toc_depth: 2
     number_sections: false
     code_folding: show
bibliography: 
  - "../input/bib/Mi_biblioteca.bib"
cls: "../input/bib/apa6.cls"
linkcolor: blue
link-citations: yes
---

@@

## _Nivel 2: Variables independientes_
  a. <div align="justify";> __S_VALPARTS: Cultura participativa de los estudiantes [AGREGADA]: How much do you agree or disagree with the following statements about student participation at school?__ (1 = Strongly agree, 2 = Agree, 3 = Disagree, 4 = Strongly disagree, 7 = Invalid, 8 = Not administered, 9 = Omitted) </div>

      * <div align="justify";> IS3G21A: Student participation in how schools are run can make schools better.</div>

      * <div align="justify";> IS3G21B: Lots of positive changes can happen in schools when students work together.</div>

      * <div align="justify";> IS3G21C: Organizing groups of students to express their opinions could help solve problems in schools.</div>

      * <div align="justify";> IS3G21D: Students can have more influence on what happens in schools if they act together rather than alone.</div>

      * <div align="justify";> IS3G21E: Voting in student elections can make a difference to what happens at schools.</div>

@@

![Distribución del conocimiento cívico](https://raw.githubusercontent.com/vjimeneza/educivic/master/output/graphs/histograma.png)

@@

![Relación entre las variables](https://raw.githubusercontent.com/vjimeneza/educivic/master/output/graphs/corrplot.png)

@@

```{r results='asis', echo=FALSE, message=FALSE}
library(texreg)
load(file = "../output/graphs/model_nulo.Rdata")
htmlreg(results_0) 
```

@@

![Influencia de la socialización de la familia y la escuela](https://raw.githubusercontent.com/vjimeneza/educivic/master/output/graphs/reg1.png)

@@

```{r results='asis', echo=FALSE}
library(texreg)

@@

![Interacción entre conocimiento cívico y nivel socioeconómico del estudiante y colegio](https://raw.githubusercontent.com/vjimeneza/educivic/master/output/graphs/interaccion.png)
